---
title: "Achoo!"
author: "Clare Gibson"
date: "2025-06-14"
format:
  gfm:
    toc: true
    toc-depth: 2
---

# Question

Can Apple Health data help me predict how many times I will sneeze in a day?

# Introduction

I am a chronic sneezer. Some days I can sneeze all day and all night long. The sneeze seems to be my body's default reaction to any kind of respiratory irritant. I have been diagnosed as having allergies to dust, grass pollen and cat hair, so my allergic sneezing happens all year round. On top of that, whenever I get any kind of respiratory virus (cold, flu, Covid), sneezing is my number one symptom.

Since 1 May 2025 I have been keeping count of the number of times I sneeze per day. I started doing this primarily to track which days were my particularly bad "attack" days, but because I also wear an Apple Watch, I wondered if I might be able to discover any patterns within my health data that might help to predict my sneeze count. It's also an opportunity for me to practise some data science.

## Packages

The code chunk below loads all of the packages needed for this analysis.

```{r}
#| label: load-packages
#| warnings: false
#| output: false

# Load packages
library(here)
library(tidyverse)
library(janitor)
library(googlesheets4)
```

## Data

The data for this analysis is located in [Google Drive](https://docs.google.com/spreadsheets/d/1pU1wmIuUt1oS-5W6xpchRRMMRrHrKT8KYfvK1saLri0/edit?usp=sharing).

```{r}
#| label: load-data
#| output: false

# Read data into a dataframe
sneezes_raw <- read_sheet(
  ss = "https://docs.google.com/spreadsheets/d/1pU1wmIuUt1oS-5W6xpchRRMMRrHrKT8KYfvK1saLri0/edit?gid=0#gid=0",
  sheet = "data"
)
```
```{r}
#| label: preview-data

# Preview the data
glimpse(sneezes_raw)
```


